### 2019-05-28 fe_px_paper/fe_body_text.tex
Updated text and figures using the corrected statistical uncertainty analysis

Using the final proton fluence at each energy position, cross sections for \ce{^{48,49,51}Cr}, \ce{^{48}V},  \ce{^{51,52m,52g,52,54,56}Mn},   \ce{^{52}Fe}, and \ce{^{55,56,57,58m,58g,58}Co}
 were extracted for (p,x) reactions  on \ce{^{nat}Fe} foils up to 55\,MeV, as recorded in \autoref{tab:fe_rp_table}.
For  (p,x) reactions on \ce{^{nat}Cu}, the (p,x) cross sections for  \ce{^{54}Mn}, \ce{^{57}Ni}, \ce{^{57,60,61}Co},   and \ce{^{60,61,64}Cu}  were extracted, as recorded in \autoref{tab:cufe_rp_table}.
For  (p,x) reactions on \ce{^{nat}Ti}, the (p,x) cross sections for  \ce{^{43}K} and \ce{^{44g,44m,44,47,48}Sc}  were extracted, as recorded in \autoref{tab:ti_rp_table}.
In addition, as there exist a number of isomers with radioactive ground states in these mass regions,  independent measurements of isomer-to-ground-state branching ratios for \ce{^{nat}Fe}(p,x)\ce{^{52m/g}Mn}, \ce{^{nat}Fe}(p,x)\ce{^{58m/g}Co}, and \ce{^{nat}Ti}(p,x)\ce{^{44m/g}Sc} were  extracted and are recorded in \autoref{tab:fe_ibr_table}.
Comparisons  of the measured cross sections and isomer branching ratios with literature data (retrieved from EXFOR\,\cite{Otuka2014272}) are seen in the figures of Appendices \ref{sec:fe_xs_figures} and \ref{sec:fe_ibr_figures}.
The propagated uncertainty in these cross sections varies widely based on the reaction product in question, with the major components  arising from uncertainty in EoB activity ($\pm$2--10\%), proton fluence ($\pm$4--9\%), and foil areal density ($\pm$0.1--0.3\%).

@@

\ce{^{48}Cr}\,($\sigma_c$)&	\makecell{0.1684\\$\pm$0.0064} &	\makecell{0.01310\\$\pm$0.00044} &	\makecell{0.00435\\$\pm$0.00018} &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	--\\
\ce{^{48}V}\,($\sigma_i$)&	\makecell{6.25\\$\pm$0.28} &	\makecell{4.41\\$\pm$0.17} &	\makecell{0.513\\$\pm$0.021} &	\makecell{0.1096\\$\pm$0.0052} &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	--\\
\ce{^{48}V}\,($\sigma_c$)&	\makecell{6.42\\$\pm$0.28} &	\makecell{4.43\\$\pm$0.17} &	\makecell{0.517\\$\pm$0.021} &	\makecell{0.1096\\$\pm$0.0052} &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	--\\
\ce{^{49}Cr}\,($\sigma_c$)&	\makecell{1.794\\$\pm$0.071} &	\makecell{2.14\\$\pm$0.13} &	\makecell{1.197\\$\pm$0.085} &	\makecell{0.315\\$\pm$0.032} &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	--\\
\ce{^{51}Mn}\,($\sigma_c$)&	\makecell{11.77\\$\pm$0.25} &	\makecell{15.69\\$\pm$0.32} &	\makecell{11.78\\$\pm$0.29} &	\makecell{6.15\\$\pm$0.25} &	\makecell{0.475\\$\pm$0.025} &	\makecell{0.68\\$\pm$0.10} &	\makecell{1.060\\$\pm$0.081} &	\makecell{1.967\\$\pm$0.067} &	\makecell{2.10\\$\pm$0.14} &	\makecell{1.981\\$\pm$0.063} &	\makecell{1.456\\$\pm$0.044} &	\makecell{0.584\\$\pm$0.025} &	-- &	--\\
\ce{^{51}Cr}\,($\sigma_i$)&	\makecell{64.1\\$\pm$4.0} &	\makecell{75.7\\$\pm$3.3} &	\makecell{56.5\\$\pm$2.5} &	\makecell{27.6\\$\pm$1.3} &	\makecell{3.83\\$\pm$0.44} &	\makecell{0.90\\$\pm$0.12} &	\makecell{0.70\\$\pm$0.11} &	\makecell{0.150\\$\pm$0.026} &	\makecell{0.067\\$\pm$0.017} &	-- &	-- &	-- &	-- &	--\\
\ce{^{51}Cr}\,($\sigma_c$)&	\makecell{75.9\\$\pm$4.0} &	\makecell{91.3\\$\pm$3.3} &	\makecell{68.3\\$\pm$2.5} &	\makecell{33.7\\$\pm$1.3} &	\makecell{4.30\\$\pm$0.44} &	\makecell{1.582\\$\pm$0.071} &	\makecell{1.760\\$\pm$0.072} &	\makecell{2.117\\$\pm$0.079} &	\makecell{2.165\\$\pm$0.096} &	\makecell{1.981\\$\pm$0.063} &	\makecell{1.456\\$\pm$0.044} &	\makecell{0.584\\$\pm$0.025} &	-- &	--\\
\ce{^{52}Fe}\,($\sigma_c$)&	\makecell{2.685\\$\pm$0.092} &	\makecell{1.733\\$\pm$0.063} &	\makecell{1.601\\$\pm$0.057} &	\makecell{2.247\\$\pm$0.078} &	\makecell{0.770\\$\pm$0.029} &	\makecell{0.2059\\$\pm$0.0099} &	\makecell{0.1920\\$\pm$0.0096} &	\makecell{0.01297\\$\pm$0.00046} &	\makecell{0.00240\\$\pm$0.00015} &	-- &	-- &	-- &	-- &	--\\
\ce{^{52m}Mn}\,($\sigma_i$)&	\makecell{8.13\\$\pm$0.28} &	\makecell{9.04\\$\pm$0.28} &	\makecell{13.69\\$\pm$0.47} &	\makecell{17.86\\$\pm$0.61} &	\makecell{23.34\\$\pm$0.79} &	\makecell{11.82\\$\pm$0.41} &	\makecell{5.78\\$\pm$0.19} &	\makecell{0.0763\\$\pm$0.0026} &	\makecell{0.0756\\$\pm$0.0033} &	\makecell{0.0754\\$\pm$0.0032} &	\makecell{0.0585\\$\pm$0.0026} &	-- &	-- &	--\\
\ce{^{52g}Mn}\,($\sigma_i$)&	\makecell{11.36\\$\pm$0.39} &	\makecell{12.82\\$\pm$0.39} &	\makecell{20.85\\$\pm$0.74} &	\makecell{28.16\\$\pm$0.98} &	\makecell{21.81\\$\pm$0.75} &	\makecell{16.32\\$\pm$0.58} &	\makecell{10.37\\$\pm$0.43} &	\makecell{0.300\\$\pm$0.011} &	\makecell{0.1113\\$\pm$0.0049} &	\makecell{0.0428\\$\pm$0.0024} &	\makecell{0.00540\\$\pm$0.00029} &	-- &	-- &	--\\
\ce{^{52}Mn}\,($\sigma_c$)&	\makecell{13.39\\$\pm$0.54} &	\makecell{14.88\\$\pm$0.74} &	\makecell{23.0\\$\pm$1.3} &	\makecell{30.9\\$\pm$1.3} &	\makecell{31.7\\$\pm$1.2} &	\makecell{18.54\\$\pm$0.87} &	\makecell{10.57\\$\pm$0.38} &	\makecell{0.313\\$\pm$0.012} &	\makecell{0.0389\\$\pm$0.0038} &	\makecell{0.0556\\$\pm$0.0029} &	\makecell{0.0185\\$\pm$0.0012} &	-- &	-- &	--\\
\ce{^{54}Mn}\,($\sigma_i$)&	\makecell{128.4\\$\pm$5.0} &	\makecell{154.4\\$\pm$6.2} &	\makecell{166.7\\$\pm$7.6} &	\makecell{129.2\\$\pm$7.4} &	\makecell{42.2\\$\pm$2.4} &	\makecell{2.46\\$\pm$0.22} &	\makecell{1.10\\$\pm$0.11} &	\makecell{1.09\\$\pm$0.13} &	\makecell{1.46\\$\pm$0.14} &	\makecell{1.53\\$\pm$0.12} &	\makecell{1.362\\$\pm$0.069} &	\makecell{1.173\\$\pm$0.055} &	\makecell{0.767\\$\pm$0.033} &	\makecell{0.0500\\$\pm$0.0046}\\
\ce{^{55}Co}\,($\sigma_i$)&	\makecell{9.25\\$\pm$0.38} &	\makecell{11.89\\$\pm$0.77} &	\makecell{15.72\\$\pm$0.80} &	\makecell{21.46\\$\pm$0.87} &	\makecell{48.4\\$\pm$2.3} &	\makecell{64.7\\$\pm$4.5} &	\makecell{61.0\\$\pm$3.5} &	\makecell{43.6\\$\pm$2.2} &	\makecell{33.2\\$\pm$2.6} &	\makecell{13.42\\$\pm$0.71} &	\makecell{0.377\\$\pm$0.021} &	\makecell{0.0436\\$\pm$0.0020} &	-- &	--\\
\ce{^{56}Mn}\,($\sigma_c$)&	-- &	\makecell{0.494\\$\pm$0.029} &	\makecell{0.610\\$\pm$0.030} &	\makecell{0.462\\$\pm$0.037} &	\makecell{0.506\\$\pm$0.046} &	\makecell{0.405\\$\pm$0.025} &	\makecell{0.2227\\$\pm$0.0079} &	\makecell{0.0962\\$\pm$0.0035} &	\makecell{0.0326\\$\pm$0.0037} &	\makecell{0.0253\\$\pm$0.0011} &	\makecell{0.01318\\$\pm$0.00093} &	-- &	-- &	--\\
\ce{^{56}Co}\,($\sigma_i$)&	\makecell{12.74\\$\pm$0.81} &	\makecell{15.5\\$\pm$1.1} &	\makecell{18.9\\$\pm$1.2} &	\makecell{23.6\\$\pm$1.1} &	\makecell{29.2\\$\pm$2.0} &	\makecell{47.8\\$\pm$2.0} &	\makecell{51.6\\$\pm$1.9} &	\makecell{82.6\\$\pm$3.2} &	\makecell{174.3\\$\pm$8.0} &	\makecell{197.3\\$\pm$8.4} &	\makecell{344\\$\pm$15} &	\makecell{389\\$\pm$15} &	\makecell{296\\$\pm$13} &	\makecell{2.95\\$\pm$0.28}\\
\ce{^{57}Co}\,($\sigma_i$)&	-- &	\makecell{0.454\\$\pm$0.040} &	\makecell{0.539\\$\pm$0.052} &	\makecell{0.648\\$\pm$0.027} &	\makecell{1.170\\$\pm$0.060} &	\makecell{1.836\\$\pm$0.070} &	\makecell{2.359\\$\pm$0.086} &	\makecell{2.50\\$\pm$0.11} &	\makecell{3.17\\$\pm$0.15} &	\makecell{3.40\\$\pm$0.15} &	\makecell{5.14\\$\pm$0.26} &	\makecell{8.46\\$\pm$0.31} &	\makecell{11.81\\$\pm$0.58} &	\makecell{4.58\\$\pm$0.42}\\
\ce{^{58m}Co}\,($\sigma_i$)&	-- &	-- &	-- &	\makecell{0.0427\\$\pm$0.0016} &	\makecell{0.0619\\$\pm$0.0023} &	\makecell{0.1054\\$\pm$0.0042} &	\makecell{0.1718\\$\pm$0.0078} &	\makecell{0.236\\$\pm$0.011} &	\makecell{0.239\\$\pm$0.012} &	\makecell{0.300\\$\pm$0.019} &	\makecell{0.475\\$\pm$0.026} &	\makecell{0.564\\$\pm$0.021} &	\makecell{0.490\\$\pm$0.022} &	\makecell{0.141\\$\pm$0.016}\\
\ce{^{58g}Co}\,($\sigma_i$)&	-- &	-- &	-- &	\makecell{0.0884\\$\pm$0.0044} &	\makecell{0.0980\\$\pm$0.0049} &	\makecell{0.1118\\$\pm$0.0057} &	\makecell{0.1229\\$\pm$0.0062} &	\makecell{0.1484\\$\pm$0.0058} &	\makecell{0.330\\$\pm$0.020} &	\makecell{0.318\\$\pm$0.016} &	\makecell{0.919\\$\pm$0.057} &	\makecell{1.320\\$\pm$0.072} &	\makecell{1.599\\$\pm$0.097} &	\makecell{0.519\\$\pm$0.048}\\
\ce{^{58}Co}\,($\sigma_i$)&	-- &	-- &	-- &	\makecell{0.1311\\$\pm$0.0047} &	\makecell{0.1599\\$\pm$0.0055} &	\makecell{0.2172\\$\pm$0.0071} &	\makecell{0.295\\$\pm$0.010} &	\makecell{0.384\\$\pm$0.012} &	\makecell{0.569\\$\pm$0.023} &	\makecell{0.618\\$\pm$0.025} &	\makecell{1.395\\$\pm$0.062} &	\makecell{1.883\\$\pm$0.075} &	\makecell{2.09\\$\pm$0.10} &	\makecell{0.660\\$\pm$0.050}\\ \bottomrule

@@

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}
\centering
\caption{Measured isomer-to-ground-state branching ratios for the various \ce{^{nat}Fe}(p,x) and \ce{^{nat}Ti}(p,x) reaction products observed in this work.}
\label{tab:fe_ibr_table}
\small
\resizebox{\textwidth}{!}{%
% \begin{tabular}{@{}lllllllllllllll@{}}
\begin{tabular}{@{}ccccccccccccccc@{}}
\toprule
                               & \multicolumn{14}{c}{Isomer branching ratio}                                                                                                                \\ \cmidrule(l){2-15} 
E$_\text{p}$ (MeV)&	\makecell{53.45\\$\pm$0.61} &	\makecell{46.63\\$\pm$0.68} &	\makecell{38.93\\$\pm$0.78} &	\makecell{34.62\\$\pm$0.85} &	\makecell{29.84\\$\pm$0.96} &	\makecell{24.4\\$\pm$1.1} &	\makecell{22.71\\$\pm$0.43} &	\makecell{19.36\\$\pm$0.56} &	\makecell{17.6\\$\pm$1.5} &	\makecell{16.54\\$\pm$0.48} &	\makecell{14.52\\$\pm$0.49} &	\makecell{12.11\\$\pm$0.53} &	\makecell{9.23\\$\pm$0.61} &	\makecell{4.10\\$\pm$0.73}\\ \midrule
\ce{^{nat}Fe}(p,x)\ce{^{52}Mn} &	\makecell{0.417\\$\pm$0.022} &	\makecell{0.414\\$\pm$0.024} &	\makecell{0.396\\$\pm$0.026} &	\makecell{0.388\\$\pm$0.021} &	\makecell{0.517\\$\pm$0.026} &	\makecell{0.420\\$\pm$0.025} &	\makecell{0.358\\$\pm$0.018} &	\makecell{0.202\\$\pm$0.010} &	\makecell{0.404\\$\pm$0.043} &	\makecell{0.638\\$\pm$0.043} &	\makecell{0.915\\$\pm$0.073} &	-- &	-- &	--\\
\ce{^{nat}Fe}(p,x)\ce{^{58}Co} &	-- &	-- &	-- &	\makecell{0.326\\$\pm$0.017} &	\makecell{0.387\\$\pm$0.020} &	\makecell{0.485\\$\pm$0.025} &	\makecell{0.583\\$\pm$0.033} &	\makecell{0.614\\$\pm$0.034} &	\makecell{0.420\\$\pm$0.026} &	\makecell{0.486\\$\pm$0.036} &	\makecell{0.341\\$\pm$0.024} &	\makecell{0.299\\$\pm$0.016} &	\makecell{0.234\\$\pm$0.015} &	\makecell{0.214\\$\pm$0.029}         \vspace{1em}     \\ 
E$_\text{p}$ (MeV)&	\makecell{53.31\\$\pm$0.61} &	\makecell{46.48\\$\pm$0.68} &	\makecell{38.76\\$\pm$0.78} &	\makecell{34.44\\$\pm$0.86} &	\makecell{29.63\\$\pm$0.96} &	\makecell{24.1\\$\pm$1.1} &	\makecell{22.29\\$\pm$0.32} &	\makecell{18.98\\$\pm$0.37} &	\makecell{17.3\\$\pm$1.5} &	\makecell{16.14\\$\pm$0.42} &	\makecell{14.03\\$\pm$0.47} &	\makecell{11.49\\$\pm$0.55} &	\makecell{8.38\\$\pm$0.70} &	\makecell{2.88\\$\pm$0.88}\\ \midrule
\ce{^{nat}Ti}(p,x)\ce{^{44}Sc} &	\makecell{0.335\\$\pm$0.022} &	\makecell{0.314\\$\pm$0.018} &	\makecell{0.291\\$\pm$0.016} &	\makecell{0.253\\$\pm$0.016} &	\makecell{0.260\\$\pm$0.015} &	\makecell{0.224\\$\pm$0.017} &	\makecell{0.345\\$\pm$0.015} &	\makecell{0.294\\$\pm$0.013} &	\makecell{0.328\\$\pm$0.026} &	\makecell{0.296\\$\pm$0.015} &	\makecell{0.252\\$\pm$0.014} &	-- &	-- &	--\\\bottomrule
\end{tabular}
}
\end{table}

>>>>

Using the final proton fluence at each energy position, cross sections for \ce{^{48,49,51}Cr}, \ce{^{48}V},  \ce{^{51,52m,52g,52,54,56}Mn},   \ce{^{52}Fe}, and \ce{^{55,56,57,58m,58g,58}Co}
 were extracted for (p,x) reactions  on \ce{^{nat}Fe} foils up to 55\,MeV, as recorded in \autoref{tab:fe_rp_table}.
For  (p,x) reactions on \ce{^{nat}Cu}, the (p,x) cross sections for  \ce{^{54}Mn}, \ce{^{57}Ni}, \ce{^{57,60,61}Co},   and \ce{^{60,61,64}Cu}  were extracted, as recorded in \autoref{tab:cufe_rp_table}.
For  (p,x) reactions on \ce{^{nat}Ti}, the (p,x) cross sections for  \ce{^{43}K} and \ce{^{44g,44m,44,47,48}Sc}  were extracted, as recorded in \autoref{tab:ti_rp_table}.
In addition, as there exist a number of isomers with radioactive ground states in these mass regions,  independent measurements of isomer-to-ground-state branching ratios for \ce{^{nat}Fe}(p,x)\ce{^{52m/g}Mn}, \ce{^{nat}Fe}(p,x)\ce{^{58m/g}Co}, and \ce{^{nat}Ti}(p,x)\ce{^{44m/g}Sc} were  extracted and are recorded in \autoref{tab:fe_ibr_table}.
Comparisons  of the measured cross sections and isomer branching ratios with literature data (retrieved from EXFOR\,\cite{Otuka2014272}) are seen in the figures of Appendices \ref{sec:fe_xs_figures} and \ref{sec:fe_ibr_figures}.
The propagated uncertainty in these cross sections varies widely based on the reaction product in question, with the major components  arising from uncertainty in EoB activity ($\pm$2--10\%), proton fluence ($\pm$5--13\%), and foil areal density ($\pm$0.1--0.3\%).

@@

\ce{^{48}Cr}\,($\sigma_c$)&	\makecell{0.172\\$\pm$0.011} &	\makecell{0.01376\\$\pm$0.00080} &	\makecell{0.00435\\$\pm$0.00029} &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	--\\
\ce{^{48}V}\,($\sigma_i$)&	\makecell{6.38\\$\pm$0.43} &	\makecell{4.64\\$\pm$0.29} &	\makecell{0.513\\$\pm$0.035} &	\makecell{0.1096\\$\pm$0.0080} &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	--\\
\ce{^{48}V}\,($\sigma_c$)&	\makecell{6.55\\$\pm$0.43} &	\makecell{4.65\\$\pm$0.29} &	\makecell{0.517\\$\pm$0.035} &	\makecell{0.1096\\$\pm$0.0080} &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	--\\
\ce{^{49}Cr}\,($\sigma_c$)&	\makecell{1.83\\$\pm$0.12} &	\makecell{2.25\\$\pm$0.18} &	\makecell{1.20\\$\pm$0.11} &	\makecell{0.315\\$\pm$0.036} &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	--\\
\ce{^{51}Mn}\,($\sigma_c$)&	\makecell{11.77\\$\pm$0.74} &	\makecell{15.69\\$\pm$0.94} &	\makecell{11.78\\$\pm$0.77} &	\makecell{6.15\\$\pm$0.41} &	\makecell{0.475\\$\pm$0.039} &	\makecell{0.679\\$\pm$0.047} &	\makecell{1.060\\$\pm$0.063} &	\makecell{1.97\\$\pm$0.15} &	\makecell{2.10\\$\pm$0.17} &	\makecell{1.98\\$\pm$0.19} &	\makecell{1.46\\$\pm$0.13} &	\makecell{0.584\\$\pm$0.041} &	-- &	--\\
\ce{^{51}Cr}\,($\sigma_i$)&	\makecell{65.9\\$\pm$5.8} &	\makecell{81.0\\$\pm$5.9} &	\makecell{56.5\\$\pm$4.5} &	\makecell{27.6\\$\pm$2.3} &	\makecell{3.83\\$\pm$0.35} &	\makecell{0.90\\$\pm$0.12} &	\makecell{0.70\\$\pm$0.13} &	\makecell{0.150\\$\pm$0.049} &	\makecell{0.110\\$\pm$0.024} &	-- &	-- &	-- &	-- &	--\\
\ce{^{51}Cr}\,($\sigma_c$)&	\makecell{77.6\\$\pm$5.7} &	\makecell{96.7\\$\pm$5.8} &	\makecell{68.3\\$\pm$4.4} &	\makecell{33.7\\$\pm$2.3} &	\makecell{4.30\\$\pm$0.35} &	\makecell{1.58\\$\pm$0.11} &	\makecell{1.76\\$\pm$0.11} &	\makecell{2.12\\$\pm$0.13} &	\makecell{2.21\\$\pm$0.17} &	\makecell{1.98\\$\pm$0.19} &	\makecell{1.46\\$\pm$0.13} &	\makecell{0.584\\$\pm$0.041} &	-- &	--\\
\ce{^{52}Fe}\,($\sigma_c$)&	\makecell{2.74\\$\pm$0.17} &	\makecell{1.82\\$\pm$0.11} &	\makecell{1.60\\$\pm$0.10} &	\makecell{2.25\\$\pm$0.15} &	\makecell{0.770\\$\pm$0.052} &	\makecell{0.206\\$\pm$0.015} &	\makecell{0.192\\$\pm$0.013} &	\makecell{0.01297\\$\pm$0.00075} &	\makecell{0.00242\\$\pm$0.00021} &	-- &	-- &	-- &	-- &	--\\
\ce{^{52m}Mn}\,($\sigma_i$)&	\makecell{8.29\\$\pm$0.52} &	\makecell{9.49\\$\pm$0.54} &	\makecell{13.69\\$\pm$0.88} &	\makecell{17.9\\$\pm$1.2} &	\makecell{23.3\\$\pm$1.5} &	\makecell{11.82\\$\pm$0.74} &	\makecell{5.78\\$\pm$0.33} &	\makecell{0.0763\\$\pm$0.0044} &	\makecell{0.0763\\$\pm$0.0057} &	\makecell{0.0754\\$\pm$0.0061} &	\makecell{0.0585\\$\pm$0.0052} &	-- &	-- &	--\\
\ce{^{52g}Mn}\,($\sigma_i$)&	\makecell{11.58\\$\pm$0.72} &	\makecell{13.46\\$\pm$0.76} &	\makecell{20.8\\$\pm$1.3} &	\makecell{28.2\\$\pm$1.8} &	\makecell{21.8\\$\pm$1.5} &	\makecell{16.3\\$\pm$1.0} &	\makecell{10.37\\$\pm$0.64} &	\makecell{0.300\\$\pm$0.017} &	\makecell{0.1124\\$\pm$0.0085} &	\makecell{0.0428\\$\pm$0.0038} &	\makecell{0.00540\\$\pm$0.00050} &	-- &	-- &	--\\
\ce{^{52}Mn}\,($\sigma_c$)&	\makecell{13.66\\$\pm$0.90} &	\makecell{15.6\\$\pm$1.1} &	\makecell{23.0\\$\pm$1.8} &	\makecell{30.9\\$\pm$2.1} &	\makecell{31.7\\$\pm$2.2} &	\makecell{18.5\\$\pm$1.3} &	\makecell{10.57\\$\pm$0.62} &	\makecell{0.313\\$\pm$0.019} &	\makecell{0.0393\\$\pm$0.0045} &	\makecell{0.0556\\$\pm$0.0048} &	\makecell{0.0185\\$\pm$0.0019} &	-- &	-- &	--\\
\ce{^{54}Mn}\,($\sigma_i$)&	\makecell{131.0\\$\pm$8.5} &	\makecell{162\\$\pm$10} &	\makecell{167\\$\pm$12} &	\makecell{129\\$\pm$10} &	\makecell{42.2\\$\pm$3.4} &	\makecell{2.46\\$\pm$0.25} &	\makecell{1.10\\$\pm$0.13} &	\makecell{1.09\\$\pm$0.14} &	\makecell{1.47\\$\pm$0.17} &	\makecell{1.53\\$\pm$0.16} &	\makecell{1.36\\$\pm$0.12} &	\makecell{1.133\\$\pm$0.080} &	\makecell{0.747\\$\pm$0.075} &	\makecell{0.0600\\$\pm$0.0080}\\
\ce{^{55}Co}\,($\sigma_i$)&	\makecell{9.43\\$\pm$0.63} &	\makecell{12.5\\$\pm$1.0} &	\makecell{15.7\\$\pm$1.2} &	\makecell{21.5\\$\pm$1.5} &	\makecell{48.4\\$\pm$3.6} &	\makecell{64.7\\$\pm$5.6} &	\makecell{61.0\\$\pm$4.5} &	\makecell{43.6\\$\pm$3.0} &	\makecell{33.6\\$\pm$3.4} &	\makecell{13.4\\$\pm$1.2} &	\makecell{0.377\\$\pm$0.035} &	\makecell{0.0421\\$\pm$0.0029} &	-- &	--\\
\ce{^{56}Mn}\,($\sigma_c$)&	-- &	\makecell{0.518\\$\pm$0.039} &	\makecell{0.610\\$\pm$0.044} &	\makecell{0.462\\$\pm$0.045} &	\makecell{0.506\\$\pm$0.054} &	\makecell{0.405\\$\pm$0.033} &	\makecell{0.223\\$\pm$0.013} &	\makecell{0.0962\\$\pm$0.0056} &	\makecell{0.0329\\$\pm$0.0043} &	\makecell{0.0253\\$\pm$0.0021} &	\makecell{0.0132\\$\pm$0.0014} &	-- &	-- &	--\\
\ce{^{56}Co}\,($\sigma_i$)&	\makecell{13.0\\$\pm$1.1} &	\makecell{16.3\\$\pm$1.4} &	\makecell{18.9\\$\pm$1.6} &	\makecell{23.6\\$\pm$1.7} &	\makecell{29.2\\$\pm$2.6} &	\makecell{47.8\\$\pm$3.2} &	\makecell{51.6\\$\pm$3.0} &	\makecell{82.6\\$\pm$5.0} &	\makecell{176\\$\pm$13} &	\makecell{197\\$\pm$16} &	\makecell{344\\$\pm$30} &	\makecell{376\\$\pm$24} &	\makecell{288\\$\pm$29} &	\makecell{3.54\\$\pm$0.47}\\
\ce{^{57}Co}\,($\sigma_i$)&	-- &	\makecell{0.476\\$\pm$0.047} &	\makecell{0.539\\$\pm$0.060} &	\makecell{0.648\\$\pm$0.044} &	\makecell{1.170\\$\pm$0.090} &	\makecell{1.84\\$\pm$0.12} &	\makecell{2.36\\$\pm$0.14} &	\makecell{2.50\\$\pm$0.16} &	\makecell{3.20\\$\pm$0.25} &	\makecell{3.40\\$\pm$0.28} &	\makecell{5.14\\$\pm$0.47} &	\makecell{8.18\\$\pm$0.52} &	\makecell{11.5\\$\pm$1.2} &	\makecell{5.49\\$\pm$0.73}\\
\ce{^{58m}Co}\,($\sigma_i$)&	-- &	-- &	-- &	\makecell{0.0427\\$\pm$0.0028} &	\makecell{0.0619\\$\pm$0.0042} &	\makecell{0.1054\\$\pm$0.0069} &	\makecell{0.172\\$\pm$0.011} &	\makecell{0.236\\$\pm$0.015} &	\makecell{0.241\\$\pm$0.019} &	\makecell{0.300\\$\pm$0.028} &	\makecell{0.475\\$\pm$0.044} &	\makecell{0.545\\$\pm$0.035} &	\makecell{0.477\\$\pm$0.049} &	\makecell{0.170\\$\pm$0.025}\\
\ce{^{58g}Co}\,($\sigma_i$)&	-- &	-- &	-- &	\makecell{0.0884\\$\pm$0.0066} &	\makecell{0.0980\\$\pm$0.0074} &	\makecell{0.1118\\$\pm$0.0082} &	\makecell{0.1229\\$\pm$0.0084} &	\makecell{0.1484\\$\pm$0.0090} &	\makecell{0.333\\$\pm$0.028} &	\makecell{0.318\\$\pm$0.027} &	\makecell{0.919\\$\pm$0.090} &	\makecell{1.276\\$\pm$0.096} &	\makecell{1.56\\$\pm$0.17} &	\makecell{0.623\\$\pm$0.083}\\
\ce{^{58}Co}\,($\sigma_i$)&	-- &	-- &	-- &	\makecell{0.1311\\$\pm$0.0072} &	\makecell{0.1599\\$\pm$0.0086} &	\makecell{0.217\\$\pm$0.011} &	\makecell{0.295\\$\pm$0.014} &	\makecell{0.384\\$\pm$0.018} &	\makecell{0.574\\$\pm$0.034} &	\makecell{0.618\\$\pm$0.039} &	\makecell{1.39\\$\pm$0.10} &	\makecell{1.82\\$\pm$0.10} &	\makecell{2.04\\$\pm$0.18} &	\makecell{0.792\\$\pm$0.086}\\ \bottomrule

@@

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}
\centering
\caption{Measured isomer-to-ground-state branching ratios for the various \ce{^{nat}Fe}(p,x) and \ce{^{nat}Ti}(p,x) reaction products observed in this work.}
\label{tab:fe_ibr_table}
\small
\resizebox{\textwidth}{!}{%
% \begin{tabular}{@{}lllllllllllllll@{}}
\begin{tabular}{@{}ccccccccccccccc@{}}
\toprule
                               & \multicolumn{14}{c}{Isomer branching ratio}                                                                                                                \\ \cmidrule(l){2-15} 
E$_\text{p}$ (MeV)&	\makecell{53.45\\$\pm$0.61} &	\makecell{46.63\\$\pm$0.68} &	\makecell{38.93\\$\pm$0.78} &	\makecell{34.62\\$\pm$0.85} &	\makecell{29.84\\$\pm$0.96} &	\makecell{24.4\\$\pm$1.1} &	\makecell{22.71\\$\pm$0.43} &	\makecell{19.36\\$\pm$0.56} &	\makecell{17.6\\$\pm$1.5} &	\makecell{16.54\\$\pm$0.48} &	\makecell{14.52\\$\pm$0.49} &	\makecell{12.11\\$\pm$0.53} &	\makecell{9.23\\$\pm$0.61} &	\makecell{4.10\\$\pm$0.73}\\ \midrule
\ce{^{nat}Fe}(p,x)\ce{^{52}Mn} &	\makecell{0.417\\$\pm$0.038} &	\makecell{0.414\\$\pm$0.037} &	\makecell{0.396\\$\pm$0.040} &	\makecell{0.388\\$\pm$0.037} &	\makecell{0.517\\$\pm$0.049} &	\makecell{0.420\\$\pm$0.040} &	\makecell{0.358\\$\pm$0.029} &	\makecell{0.202\\$\pm$0.017} &	\makecell{0.404\\$\pm$0.056} &	\makecell{0.638\\$\pm$0.076} &	\makecell{0.92\\$\pm$0.12} &	-- &	-- &	--\\
\ce{^{nat}Fe}(p,x)\ce{^{58}Co} &	-- &	-- &	-- &	\makecell{0.326\\$\pm$0.028} &	\makecell{0.387\\$\pm$0.034} &	\makecell{0.485\\$\pm$0.040} &	\makecell{0.583\\$\pm$0.047} &	\makecell{0.614\\$\pm$0.049} &	\makecell{0.420\\$\pm$0.041} &	\makecell{0.486\\$\pm$0.055} &	\makecell{0.341\\$\pm$0.040} &	\makecell{0.299\\$\pm$0.026} &	\makecell{0.234\\$\pm$0.031} &	\makecell{0.214\\$\pm$0.039}\\         \vspace{1em}     \\ 
E$_\text{p}$ (MeV)&	\makecell{53.31\\$\pm$0.61} &	\makecell{46.48\\$\pm$0.68} &	\makecell{38.76\\$\pm$0.78} &	\makecell{34.44\\$\pm$0.86} &	\makecell{29.63\\$\pm$0.96} &	\makecell{24.1\\$\pm$1.1} &	\makecell{22.29\\$\pm$0.32} &	\makecell{18.98\\$\pm$0.37} &	\makecell{17.3\\$\pm$1.5} &	\makecell{16.14\\$\pm$0.42} &	\makecell{14.03\\$\pm$0.47} &	\makecell{11.49\\$\pm$0.55} &	\makecell{8.38\\$\pm$0.70} &	\makecell{2.88\\$\pm$0.88}\\ \midrule
\ce{^{nat}Ti}(p,x)\ce{^{44}Sc} &	\makecell{0.335\\$\pm$0.029} &	\makecell{0.314\\$\pm$0.024} &	\makecell{0.291\\$\pm$0.025} &	\makecell{0.253\\$\pm$0.023} &	\makecell{0.260\\$\pm$0.023} &	\makecell{0.224\\$\pm$0.023} &	\makecell{0.345\\$\pm$0.024} &	\makecell{0.294\\$\pm$0.021} &	\makecell{0.328\\$\pm$0.034} &	\makecell{0.296\\$\pm$0.028} &	\makecell{0.252\\$\pm$0.027} &	-- &	-- &	--\\ \bottomrule
\end{tabular}
}
\end{table}
